CSci487 Penetration Testing Project: AILEE

### 2019-05-04 csci487/project/paper.tex
Add figures; small changes to paper
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

\author{\IEEEauthorblockN{Grant Haataja}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
grant.haataja@und.edu}
\and
\IEEEauthorblockN{David Wilson}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
david.andrew.wilson@und.edu}
\and
\IEEEauthorblockN{Michael Turnbull}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, USA \\
michael.turnbull@und.edu}
}

@@

@@

@@

In particular, the \textit{exploit} command is extremely useful for gaining access to other computers. This command is similar to the Metasploit framework which is commonly used in real-life penetration testing. In the game, it only has two possible exploits to choose from, and if ran against a vulnerable IP address with the proper port selection, will successfully open a new shell on the target computer.

@@

@@

This is the code for the structure and mechanics of the computer filesystems.

>>>>

\author{\IEEEauthorblockN{Grant Haataja}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, ND, USA \\
grant.haataja@und.edu}
\and
\IEEEauthorblockN{David Wilson}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Grand Forks, ND, USA \\
david.andrew.wilson@und.edu}
\and
\IEEEauthorblockN{Michael Turnbull}
\IEEEauthorblockA{\textit{UND Computer Science} \\
Monroe, NH, USA \\
michael.turnbull@und.edu}
}

@@

\tableofcontents

@@

\begin{figure}[h]
    \centerline{\includegraphics[scale=0.7]{shellloop.png}}
    \caption{Shell flow diagram}
    \label{fig:shell-flow}
\end{figure}

@@

In particular, the \texttt{exploit} command is extremely useful for gaining access to other computers.  This command is similar to the Metasploit framework, commonly used in real-life penetration testing.  In the game, as the player uncovers exploits in different computers with the \texttt{vscan} command, those exploits are added to a global database of exploits which the user can then pick from in the \texttt{exploit} command.  Exploits are specific to a port on a computer, and if correctly used, will successfully open a new shell on the target computer.

@@

\begin{figure}[hp]
    \centerline{\includegraphics[scale=0.5]{gameflow.png}}
    \caption{The sequence of events in play order}
    \label{fig:gameplay-sequence}
\end{figure}

@@

This is the code for the structure and mechanics of the computer filesystems. 
Similar to Linux, both files and folders have and use discrete permissions, 
marking certain files as executable and readable.  While there are not yet any
provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
the permissions architecture is in place for adding future file-editing
utilities.

Executable files are created from a separate filesystem constructor.  Each
executable file simply is a \texttt{File} object with the executable bit set in
its permissions object, and the file contents are pure Python code that executes
when the file is run via the \texttt{run} command.  To verify that arbitrary
code is not run (which would break the game), executable files compare hashes
from creation to runtime to and will not run if the contents have been
altered.
